### 2021-11-17 documentos/generators.tex
Committing fixes in the dark, seriously, who killed my power!?

\janote{\colorbox{yellow}{¡¡¡Léeme Carlos!!!:} Las frases nuevas que hacen
parte del esqueleto y que no estaban ayer, martes, son las que aparecen 
en las líneas 412, 422 y 425.}

There exists a subset of PCE quantum channels that generate 
all PCE's, and the existence of these PCE generators may be explained with 
the vector space point of view.
\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
By standard theorems of linear algebra, any subspace $W$ can be extended to a
maximal (non-trivial) subspace of dimension $2N-1$ by adjoining appropriate
additional basis elements. This can clearly be done in different ways. We
therefore arrive to the set of maximal extensions of $W$. Clearly, the
intersection of all the elements of this set reduces to $W$ itself, leading to
the result that all PCE's can be obtained as intersections of maximal PCE's. 
\janote{Referenciar \Fref{fig:examplesPCE} y apéndice con una ilustración 
del caso de 2 qubits usando los $\mcG$. Mostrar en ese apéndice todos
los generadores de 2 qubits}

PCE generators may be characterized with a unique vector index
$\vec\alpha$, and therefore, denoted as $\pceg$.

For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
verified by Siudzińska~\cite{siudzinska2019geometry}.
\janote{Esto puede
ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}

@@

PCE generators $\pceg$ (and so $\san$'s rows and columns) obey a symmetry rule
that defines uniquely every PCE generator.

PCE generators $\pceg$ may be classified by its local action on 
all individual qubits in the system.

>>>>

There exists a subset of PCE quantum channels that generate 
all PCE's, and the existence of these PCE generators may be explained with 
the vector space point of view.
\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
By standard theorems of linear algebra, any subspace $W$ can be extended to a
maximal (non-trivial) subspace of dimension $2N-1$ by adjoining appropriate
additional basis elements. This can clearly be done in different ways. We
therefore arrive to the set of maximal extensions of $W$. Clearly, the
intersection of all the elements of this set reduces to $W$ itself, leading to
the result that all PCE's can be obtained as intersections of maximal PCE's. 
\janote{Referenciar \Fref{fig:examplesPCE} y apéndice con una ilustración 
del caso de 2 qubits usando los $\mcG$. Mostrar en ese apéndice todos
los generadores de 2 qubits}
For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
verified by Siudzińska~\cite{siudzinska2019geometry}.
\janote{Esto puede
ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}

PCE generators may be characterized with a unique vector index
$\vec\alpha$, and therefore, denoted as $\pceg$. El numero de generadores 
concide con esa vaina. 
PCE generators $\pceg$ may be classified by its local action on 
all individual qubits in the system.
\cpnote{Acuerdate de la referencia a la figura 4}

@@

PCE generators $\pceg$ (and so $\san$'s rows and columns) obey a symmetry rule
that defines uniquely every PCE generator.
\cpnote{Acuerdate de otra referencia a la figura 4}
